---
title: "02_Higino"
author: "Gracielle Higino"
date: "2019-10-16"
# knit: (function(inputFile, encoding) {
#       out_dir <- 'manuscript';
#       rmarkdown::render(inputFile,
#                         encoding = encoding,
#                         output_file = file.path(dirname(inputFile),
#                         out_dir,
#                         'manuscript.docx')) })
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
      # word_document:
  #   reference_docx: manuscript/sources/template.docx
csl: manuscript/sources/ecology-letters.csl
bibliography:
- manuscript/sources/library.bib
- manuscript/sources/installed-r-packages.bib
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# http://stackoverflow.com/questions/28894515/rmarkdown-directing-output-file-into-a-directory
out_dir <- 'manuscript'
if(!file.exists(out_dir)) {
  dir.create(out_dir)
}
```



```{r r_packages, include = FALSE}
# ipak function: install and load multiple R packages.
# Check to see if packages are installed.
# Install them if they are not, then load them into the R session.
# https://gist.github.com/stevenworthington/3178163

ipak <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg))
    {
      install.packages(new.pkg,
                       dependencies = TRUE,
                       repos = "https://cloud.r-project.org")
    }
    suppressPackageStartupMessages(sapply(pkg, require, character.only = TRUE))
}

ipak(packages_list <- c(
                       "devtools",  # required; do not exclude from this list
                       "bibtex",    # required; do not exclude from this list
                       "knitr",     # required; do not exclude from this list
                       "rmarkdown", # required; do not exclude from this list
                       "pacman",    # required; do not exclude from this list
                       "captioner", # required; do not exclude from this list
                       "git2r",     # required; do not exclude from this list
                       "ggplot2",
                       "dplyr",
                       "tidyr",
                       "readr")
     )

pacman::p_load_gh(char = c(
                           # required; do not exclude from this list
                           "benmarwick/wordcountaddin",
                           # required; do not exclude from this list
                           "ropensci/rcrossref"
                           ),
                  install = TRUE,
                  dependencies = TRUE)

write.bib(packages_list, "manuscript/sources/installed-r-packages.bib")

fig <- captioner(prefix ="Figure")
tab <- captioner(prefix="Table")
```

# Loading the data:
```{r, warnings=FALSE, results='hide', cache.comments=FALSE}
emperors <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-13/emperors.csv")
```

# Who kills emperors usually?
```{r}
ggplot(data = emperors, aes(x=killer)) +
  geom_bar(stat="count") +
  theme(axis.text.x = element_text(angle = 90))
```


# Arhama: Is there a relation between the emperor rise and who kills him?

```{r}
E = emperors %>%
       select(name,rise,killer)%>%
          arrange (name)
E
ggplot(E, aes(x=killer)) +
  geom_point(stat="count") + theme_dark() +theme(axis.text.x = element_text(angle = 90))+
  facet_wrap(~rise)
```


# Are causes of killing related to where do you were born?

```{r}
ggplot(emperors, aes(x=killer)) +
  geom_bar(stat="count") +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~birth_prv)
```

Well, we can tell that if you were an Emperor born in Italy and your power was given to you as a right at your birth, you are very much in trouble. Anything can kill you, so you better sleep with an eye open.

However, if you were born, say, in Pannonia Inferior and was elected, or even bought your position, you are pretty much safe.

Can we predict what will happen with the next ancient roman emperors that will never born because, well, then they wouldn't be ancient?



# R packages

```{r eval = TRUE, echo = FALSE, results='asis'}
cite_pkg <- function(pkg_list) {

  packages <- sort(pkg_list)
  cites <- lapply(packages, utils::citation)
  cites.bib <- lapply(cites, utils::toBibtex)

  # generate reference key
  for (i in seq_len(length(cites.bib))) {
    cites.bib[[i]] <-
      sub(
        pattern = "\\{,$",
        replacement = paste0("{", packages[i], ","),
        x = cites.bib[[i]]
      )
  }

  # write bibtex references to file
  writeLines(enc2utf8(unlist(cites.bib)), con = "manuscript/sources/pkg-refs.bib", useBytes = TRUE)

  # return named list of bibtex references
  names(cites.bib) <- packages # pkgs

  writeLines(paste("- ", names(cites.bib), " [@", names(cites.bib), "]", sep = ""))
}


cite_pkg(packages_list)
```



# References

<!-- https://stackoverflow.com/a/44294306/5974372 -->

<div id="refs"></div>



```{r session-info}
sessionInfo()
```
